%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Engineering Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Satcom Resources} % Organization
    {Avon, CO} % Location
    {June 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improving the speed and reliability of orders through software automation.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dynamics Engineer} % Job title
    {SpaceX} % Organization
    {Hawthorne, CA} % Location
    {April 2015 - December 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Doubled the reliability and halved the time of test specification creation by designing and implementing a data analysis and data visualization software package using mainly Python, Pandas and Numpy. This allowed engineers to work with large data sets more efficiently leading to more accurate test specifications.}
        \item {Deployed Python package to production level Pip accessible repository with continuous deployment, automatic testing, and automatic documentation generation using Bamboo, PyLint, Tox, and Sphinx.}
        \item {Decreased review time of technical documents by deploying a Jupyter Notebook application to AWS GovCloud for Dynamicists to use the Python package’s data structure, math utilities, data aggregation tools, and data visualization sub-package in a sharable and easily accessible and followable document.}
        \item {Decreased flight risk by writing Python scripts that queried thousands of vibration tests and checked against new testing standards for Flight 21(the rocket that landed) ensuring all vibration susceptible components were safe for flight.}
        \item {Mitigated component susceptibility to high frequency dynamics by working with designers, predicting vibration and shock environments through data aggregation of test and flight data, and implementing vibration tests to qualify hardware before flight.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Dynamics Intern} % Job title
    {SpaceX} % Organization
    {Hawthorne, CA} % Location
    {May 2013 - November 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Determined shock and vibration environments for propulsion, avionic, and structural components on the Falcon 9 rocket and Dragon capsule. Followed by assisting with the testing and verification of these component environments.}
        \item {Improved accuracy of shock environments by implementing and analyzing several large scale shock tests to determine shock susceptibility of components.}
        \item {Improved speed and reliability of data reviews by developing automated reports in Matlab.}
      \end{cvitems} 
    }

%---------------------------------------------------------
  \cventry
    {Member of 6 person team} % Job title
    {eSolar Inc.} % Organization
    {Burbank, CA} % Location
    {Fall 2013 - Summer 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed, built, and tested a data acquisition and instrumentation package to measure wind loads on heliostats.}
        \item {Wrote data processing code to get force data on heliostats, sync timing from multiple data sources, and present the data in a useful form, followed by putting this data into a database for further use.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Member of 5 person team} % Job title
    {Skyline Eco-Adventures} % Organization
    {Claremont, CA} % Location
    {Fall 2014 - Winter 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed prototype of adjustable braking trolley to control velocity of zipline participants.}
        \item {Wrote trolley simulation code in Matlab that allowed the team to effectively evaluate design alternatives.}
      \end{cvitems}
    }

%---------------------------------------------------------

\end{cventries}
